Thoughts on resubmission within ARC1

### 2009-03-13 doc/client/client_technical.tex
fixed small bug

\begin{shaded}
\begin{verbatim}
<CacheCheckResponse>
   <CacheCheckResult>
   <Result>
         <FileURL>http://knowarc1.grid.niif.hu/storage/Makefile</FileURL>
         <ExistInTheCache>true</ExistInTheCache>
         <FileSize>30</FileSize>
   </Result>
   <Result>
         <FileURL>http://knowarc1.grid.niif.hu/storage/Makefile</FileURL>
         <ExistInTheCache>true</ExistInTheCache>
         <FileSize>30</FileSize>
   </Result>
  </CacheCheckResult>
</CacheCheckResponse>
\end{verbatim}
\end{shaded}

>>>>

\begin{shaded}
\begin{verbatim}
<CacheCheckResponse>
   <CacheCheckResult>
   <Result>
         <FileURL>http://knowarc1.grid.niif.hu/storage/Makefile</FileURL>
         <ExistInTheCache>true</ExistInTheCache>
         <FileSize>190</FileSize>
   </Result>
   <Result>
         <FileURL>ftp://download.nordugrid.org/test/README</FileURL>
         <ExistInTheCache>true</ExistInTheCache>
         <FileSize>176</FileSize>
   </Result>
  </CacheCheckResult>
</CacheCheckResponse>
\end{verbatim}
\end{shaded}
